### 2020-03-02 doc/icfp20/intro.tex
more tweaks

We make use of and extend~\citet{MusicTools}, a library of small tools
for analysis and synthesis of music written in Agda, with the goal of
eventually being a dependently-typed alternative to Euterpea.
Previous work by \citet{cong-cp} using Music Tools expresses
first-species counterpoint with the Agda type system, so that an error
in counterpoint resulted in an Agda type error. Although this takes
advantage of Agda's native type checking, it has several
downsides. One is that the Agda errors may be difficult to interpret
as the corresponding musical error. Another is that it is difficult to
keep the types both simple and flexible.

In this work we present an alternative representation of counterpoint
using what could be considered a custom musical type checker written
in Agda. This allows us to easily describe fine-grained rules, write
custom type errors, and then combine subsets of rules together for
larger-scale checking. Music can be easily combined with rules it
satisfies as a dependent record type. This record represents a proof
certificate that the music follows the asserted rules.
Rules can also easily be used in
other contexts, satisfying modularity and composability.

@@

This is an experience report, and we highlight both the advantages and
disadvantages of using Agda for music theory. On one hand the
expressiveness of dependent types makes it easy and natural to
describe music theory rules. However we find the emphasis on proof
construction and particularly the extra work needed for decidable
equality can add an extra burden which is not always welcome. However
overall we feel the positives far outweigh the negatives, and in the
final section we describe future work which may help reduce the tedium.

>>>>

We make use of and extend Music Tools~\citep{MusicTools},
a library of small tools
for analysis and synthesis of music written in Agda, with the goal of
eventually being a dependently-typed alternative to Euterpea.
Previous work by \citet{cong-cp} expresses
first-species counterpoint with the Agda type system, so that an error
in counterpoint resulted in an Agda type error. Although this takes
advantage of Agda's native type checking, it has several
downsides. One is that the Agda errors may be difficult to interpret
as the corresponding musical error. Another is that it is difficult to
keep the types both simple and flexible.

In this work we present an alternative representation of counterpoint
using what could be considered a custom musical type checker written
in Agda. This allows us to easily describe fine-grained rules, write
custom type errors, and then combine subsets of rules together for
larger-scale checking. Music can be easily combined with rules it
satisfies as a dependent record type. This record represents a proof
certificate that the music follows the asserted rules.
Rules can also be used in multiple different contexts, satisfying
modularity and composability.

@@

This is an experience report, and we highlight both the advantages and
disadvantages of using Agda for music theory. On one hand the
expressiveness of dependent types makes it easy and natural to
describe music theory rules. On the other hand we find the emphasis on proof
construction and particularly the extra work needed for decidable
equality can add an extra burden which is not always welcome. However
overall we feel the positives far outweigh the negatives, and in the
final section we describe future work which may help reduce the tedium.
